\section{TA Evaluation UI Improvements}

\subsection{View Submissions UI}
An interface for the instructors/TAs to see all the list of submissions ordered in student groups. All the students in the groups are shown as a list and A status of whether they submitted explicitly, or was timed out is shown. This helps an instructor to verify that a group had indeed submitted before they leave the hall. The Deadline of the assignment is also shown on the top.

\subsection{Evaluation interface}

\begin{enumerate}
\item A static panel has been added which contains all the navigation buttons and the the submitted files download options which are essential and frequently required during evalution by the TA's and the instructor. This panel has been optimally designed to occupy minimum space so as to not interfere with the viewability of the report as well to provide maximum usability.
\item The static panel contains next and previous buttons for the TA's. The TA's can easily navigate through all the submissions of each group using these buttons. It provides much improvements than the previous "Search for student" interface.
\item An colour coded index had been added to easily access particular questions, and the colour denotes the status of evaluation. "Green" coloured background denotes that the question has been already evaluated. "White" coloured background means that the question is yet to be evaluated.
\end{enumerate}

TODO: Marks to be set as zero if not answered.

\subsection{Jump to questions, easy navigation}
The paned shows links to all question on the right side which can be clicked to easily navigate to that question.