\section{Objectives}
\begin{enumerate}
\item Facilitate Group Assignments

There should be a feature in the app that enables the students to do lab assignments in groups.

\item Support Explicit Finishing of Lab Exam

Students should be able to explicitly finish their lab examinations before leaving the lab so that they can't edit it afterwards.

\item Upload Additional Files by Instructor

Instructor must be able to upload additional helper files/sample code that are required in lab exams/assignments.

\item Improve Interface for TA Evaluation

The evaluation interface for TAs need lots of improvements. Major requirements are:
	\begin{itemize}
	\item Currently, TAs have to search for the student-name to open his/her paper for evaluation and to download files submitted by them. There should be a more usable interface where all the group submissions are listed.
	\item Within an answer sheet, there should be a static panel that has options to navigate to other groups' submissions and to download submitted files. %that has options for `go to next answer sheet', `go to previous answer sheet', and `download submitted files'.
	\item The TA has to scroll to every question for evaluation. There should be a static index panel which enables easy navigation to the required question.
	\item There should be a way for the TA's to identify questions which are yet to be evaluated.
	\item If an answer is not present, it should be automatically given zero marks and flagged as evaluated.
	\end{itemize}

\item Better UI for Edit/Delete Labs

The interface for editing/deleting labs is difficult to use. The same form (on top of the page) is used for creating a new lab and for editing/deleting an existing lab. The instructor has to scroll down to the required lab, read the details, scroll back up, and enter them into the form. Same for deleting a lab. An intuitive interface for modifying/deleting the labs is required.

\item Improve Student-Files Upload Interface

The students cannot see the files they have uploaded. They just get a message ``File has been uploaded'' without any visible cue to verify even the file name. A feature is required where the students can see the list of files they have uploaded and verify the content.

\item Remove Alert Box Pop-ups from Student and TA Interfaces

While students are answering the questions or TAs are evaluating answer sheets, everytime they save an answer/comment, a javascript alert box pops up saying that the data has been saved. The user has to click OK every time. This is redundant, unnecessary, and annoying (not a good user experience). The alert box should be replaced with a message display where a user interaction is not required.

\end{enumerate}

